Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Updated related work and references

\section{Related Work}
With the rapid usage increase of online photo storage and social media
on sites like Facebook, Flickr and Picasa, more image data is
available than ever before, and is growing every day.  Every minute
27800 photos are uploaded to Instagram, while Facebook receives
208,300 photos over the same time frame.\cite{Horaczek2013} This alone
provides a source of image data that can scale into the billions.  The
explosion of available images on social media has motivated image
processing research and application development that can take
advantage of very large image data stores.

\cite{White2010} presents a case study of classifying and clustering billions of regular images using MapReduce. It describes an image pre-processing technique for use in a sliding-window approach for object recognition.  Distributed High Performance Video Processing in the cloud outlines some of the limitations of the MapReduce model when dealing with high-speed video encoding, namely its dependence on the NameNode as a single point of failure, and lack of possibility for generalization in order to suit the issue at hand. An alternate optimized implementation is proposed for providing cloud-based IaaS (Infrastructure as a Service) Solution. In Parallel K-Means clustering of Remote Sensing Images Based on MapReduce \cite{Lv2010} describe using the k-means algorithm in conjunction with MapReduce and satellite/aerophoto images in order to find different elements based on their color. Using Transaction Based Parallel computing to solve image processing and computational physics problems by Harold describes the use of distributed computing with two examples video processing and subsurface transport. There was no information provided on how image processing parts of the examples.

	Case Study of Scientific Data Processing on a Cloud Using Hadoop \cite{Zhang2010} present methods used for processing sequences of microscope images of live cells. The images are relatively small 512x512 16-bit pixels, stored in 90 MB folders there were some issues regarding to fitting into Hadoop DFS blocks with were solved by custom InputFormat, InputSplit and Record Reader classes. A scalable image processing framework for gigapixel Mars and other celestial body images by Mark Powell describes the way NASA handles image processing of celestial images captured by the Mars Orbiter and rovers. Clear and concise descriptions are provided about the segmentation of gigapixel images into tiles, how the tiles are processed and how image processing framework handles scaling and works with the distributed processing. Ultra-fast processing of gigapixel tissue microarray images using high performance computing \cite{Wang2011} about the speeding up the analysis of Tissue MicroArray images by substituting human expert analysis for automated processing algorithms. While the images were measured to be in gigapixels, the content is easily segmented and there was no need to focus on being able to analyze all of image at once. The work was all done on a specially build grip high performance	computing platform on Hadoop framework.

	Terabyte size image computations on Hadoop cluster \cite{Bajcsy2013} platforms present a characterization of four basic terabyte size image computations on a Hadoop Cluster in terms of their relative efficiency according to the modified Amdahls law. The work is motivated by the fact that there is a lack of 6 standard benchmarks and stress tests for big image processing operations on Hadoop framework. Terabyte-scale image search\cite{Moise2013} outlines about querying thousands of images in one run using Hadoop MapReduce framework using the MapReduced based eCP Algorithm. The experiment does an image search on 110 million images collected from web on Grid 5000 Platform. The results are evaluated in order to understand the best practices that can tune Hadoop MapReduce Performance for image search.

>>>>

\section{Related Work}
With the rapid usage increase of online photo storage and social media
on sites like Facebook, Flickr and Picasa, more image data is
available than ever before, and is growing every day.  Every minute
27800 photos are uploaded to Instagram, \cite{Horaczek2013}while Facebook receives
208,300 photos over the same time frame. This alone
provides a source of image data that can scale into the billions.  The
explosion of available images on social media has motivated image
processing research and application development that can take
advantage of very large image data stores.

White et.al \cite{White2010} presents a case study of classifying and clustering billions of regular images using MapReduce. It describes an image pre-processing technique for use in a sliding-window approach for object recognition. Pereira et.al \cite{Pereira2010} outlines some of the limitations of the MapReduce model when dealing with high-speed video encoding, namely its dependence on the NameNode as a single point of failure, and lack of possibility for generalization in order to suit the issue at hand. An alternate optimized implementation is proposed for providing cloud-based IaaS (Infrastructure as a Service) solution.  Zhenhua Lv et.al \cite{Lv2010} describe using the k-means algorithm in conjunction with MapReduce and satellite/aerophoto images in order to find different elements based on their color.

Zhang et.al \cite{Zhang2010} present methods used for processing sequences of microscope images of live cells. The images are relatively small 512x512 16-bit pixels, stored in 90 MB folders there were some issues regarding to fitting into Hadoop DFS blocks with were solved by custom InputFormat, InputSplit and RecordReader classes. Mark Powell et.al \cite{Powell2010} describes the way NASA handles image processing of celestial images captured by the Mars Orbiter and rovers. Clear and concise descriptions are provided about the segmentation of gigapixel images into tiles, how the tiles are processed and how image processing framework handles scaling and works with the distributed processing. Wang, Yinhai and McCleary\cite{Wang2011} about the speeding up the analysis of Tissue MicroArray images by substituting human expert analysis for automated processing algorithms. While the images were measured to be in gigapixels, the content is easily segmented and there was no need to focus on being able to analyze all of image at once. The work was all done on a specially build grip high performance	computing platform on Hadoop framework.

Bajcsy et.al \cite{Bajcsy2013} present a characterization of four basic terabyte size image computations on a Hadoop Cluster in terms of their relative efficiency according to the modified Amdahls law. The work is motivated by the fact that there is a lack of 6 standard benchmarks and stress tests for big image processing operations on Hadoop framework. Moise et.al \cite{Moise2013} outlines about querying thousands of images in one run using Hadoop MapReduce framework using the MapReduced based eCP Algorithm. The experiment does an image search on 110 million images collected from web on Grid 5000 Platform. The results are evaluated in order to understand the best practices that can tune Hadoop MapReduce Performance for image search.
